Methods and Results

### 2021-03-29 ms.Rmd
just updating to render docs

---
  title: "Methods and Results"
  author: 
  date: "`r Sys.Date()`"
  bibliography: refs.bib
  csl: pnas.csl
  output: 
    bookdown::html_document2:
      code_folding: hide
      number_sections: no
      toc: yes
      toc_depth: 6
      toc_float: yes
    bookdown::word_document2:
      toc: no
      toc_depth: 6
      number_sections: true
      reference_docx: template.docx
  editor_options: 
    chunk_output_type: console
---

```{r loadpackages, echo = FALSE, results = "hide"}
  pacman::p_load(tidyverse, metafor, brms, metaAidR)

@@

  model <- rma.mv(lnRR ~ 1, V = data$v_lnRR, random = list(~1|study, ~1|obs, ~1|variable, ~1|species), test = "t", data = data)

@@

  model <- rma.mv(lnRR ~ SSD_lnRR, V =  data$v_lnRR, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)

@@

  model <- rma.mv(lnRR ~ Harm_type, V = data$v_lnRR, random = list(~1|study, ~1|species, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
  robust(model, cluster = data$study)

@@

  # Note that for gestation, these data on viviparous species are restricted completely to fish only, and indirect measurements. So, confounded. It's hard to know what is the driving factor...could be parity mode, but could be also due to all being fish, or even just that they are indirect measures, also, only 7 studies.
  model <- rma.mv(lnRR ~ Gestation - 1, V = data$v_lnRR, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
  robust(model, cluster = data$study)

>>>>

---
  title: "Methods and Results"
  author: 
  date: "`r Sys.Date()`"
  bibliography: refs.bib
  csl: pnas.csl
  output: 
    bookdown::word_document2:
      toc: no
      toc_depth: 6
      number_sections: true
      reference_docx: template.docx
    bookdown::html_document2:
      code_folding: hide
      number_sections: no
      toc: yes
      toc_depth: 6
      toc_float: yes
  editor_options: 
    chunk_output_type: console
---
```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
  ## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
    ## and rounded to 2 digits      ## and rounded to 2 digits
    options(digits = 2)
```

```{r loadpackages, echo = FALSE, results = "hide"}
  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR)

@@

@@

@@

@@

  # Note that for gestation, these data on viviparous species are restricted completely to fish only, and indirect measurements. So, confounded. It's hard to know what is the driving factor...could be parity mode, but could be also due to all being fish, or even just that they are indirect measures, also, only 7 studies.
